\textsf{Are large language models superhuman chemists?}

### 2024-10-31 src/tex/appendix.tex
finalize
Former-commit-id: 9c194006e3e56a88e4dab9f3326e35b18ae5f44e

\begin{table}
    \centering
    \small
    \caption{\textbf{Examples for each of the topics considered in the evaluation of the \chembench corpus.} The table shows the percentage of questions in the corpus that belong to each topic, as well as example questions.}
    \label{tab:chembench_corpus_topic}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}

@@

        \end{tabularx}
    }
 \end{table}

>>>>

    \caption{\textbf{Examples for each of the topics considered in the evaluation of the \chembench corpus.} The table shows the percentage of questions in the corpus that belong to each topic, as well as example questions.} \label{tab:chembench_corpus_topic} \\

@@
